% resumo em inglês
\setlength{\absparsep}{18pt} % ajusta o espaçamento dos parágrafos do resumo
\begin{resumo}[Abstract]
 \begin{otherlanguage*}{english}
   Medicine is a science that shows major evolutions during evolutionary times, and there are a lot of challenges that keep on existing, trying to avoid human mistakes is one of them. It is clear that the act of making mistakes is a human characteristic and we are succinct to keep doing. In a hospital environment, human mistakes could happen due to a lot of external facts(people problems) and internal facts(hospital problems). So, It has a constant presence of Adverse Events in the hospital environment, the same problems could be avoided through notifications and, consequently, taking decisions to solve. Unfortunately, in practice, the cases are rarely notifieds due to a lot of reasons that affect health’s professionals. It is not new that many sciences have been benefited with technology, and this solution to adverse events’ problem it’s a great fit to put technology to work, one more time. The main problem here it’s the absence of notifications by the health’s professionals due to unusual ways to notify an event and the resistance of the professionals, with fear of being retaliated against by their boss. To this purpose it was made a systematic review of primary studies on the context and a lot of meetings and interviews with nursing’s teams and nursing’s academics to build a better tool. The challenge consists in turn the action of notify more usually, through a virtual process of notifications and safety, using resources to ensure anonymity during the notification of an event. Consequently, with the increase in the number of notifications, we’ll have an improvement on decision-making to solve the events.

   \vspace{\onelineskip}
 
   \noindent 
   \textbf{Keywords}: Hospitals, Adverse Events, Notifications, Mobile apps, API.
   
   \textbf{Keywords}: latex. abntex. text editoration.
 \end{otherlanguage*}
\end{resumo}